What really matters (and to whom): Investigating heterogeneous effects in high-dimensional conjoint analyses

### 2024-11-28 Manuscript files/Manuscript.qmd
Formatting

# Method
Data of the above conjoint experiment was modeled by the previously described cjbart approach.
For this, we used the R package *cjbart* described in CITE.
We fitted a BART model containing the profile attributes and various subject-level covariates: age, country, gender, and political orientation, and subjects' agreement on different statements regarding political statements (e.g., EXAMPLE).
A list of all covariates, including their type, can be found in TABLE.
This resulted in a trained BART model that was used to make the (counterfactual) predictions needed for calculating the quantities of interest, such as IMCEs or AMCEs.

```{r covariates, echo=FALSE}
#| output: asis
library(kableExtra)

@@

# Results
In @fig-amces we present the AMCEs estimated by averaging the IMCEs calculated using the cjbart model.

@@

## Integration of Results
For AMCEs, theoretically most favorable events served as baseline. As can be seen, increased attribute levels (i.e., less favourable events) were usually linked to significantly decreased levels of support. For example, increasing the risk of a nuclear strike from the reference level 'Not present (0%)' to 'Moderate (10%)' decreased the average probability of a participant choosing the latter profile by about -8.5%. The AMCE point estimates were in line with the AMCEs reported in CITE, which is why we refrain from an in-depth discussion here and refer the interested reader to CITE.
HIER WAS DAZU SCHREIBEN DAS WIR HÖHERE SEs HABEN? DAZU SCHREIBEN DIE HALT IN IHREM PAPER EH GAR NIX

@@

## Methodological Discussion
Discussion & Limitations -Tuning -Wie viele Covariates (inference vs. exploration) -Stabilität

>>>>

# Method

Data of the above conjoint experiment was modeled by the previously described cjbart approach.
For this, we used the R package *cjbart* described in CITE.
We fitted a BART model containing the profile attributes and various subject-level covariates: age, country, gender, and political orientation, and subjects' agreement on different statements regarding political statements (e.g., EXAMPLE).
A list of all covariates, including their type, can be found in @tbl-covariates.
This resulted in a trained BART model that was used to make the (counterfactual) predictions needed for calculating the quantities of interest, such as IMCEs or AMCEs.

```{r covariates, echo=FALSE}
#| echo: false
#| results: asis
#| label: tbl-covariates

library(knitr)
library(kableExtra)

covs <- data.frame(
  Covariates = c(
    "Country",
    "Age",
    "Gender",
    "Political Orientation",
    "The political agenda should focus <br> on the war against Ukraine.",
    "How scared are you by the <br> Russian war against Ukraine?",
    "Does military support of [country] matter <br> regarding your current voting intention?",
    "The US-American imperialism is <br> the real threat to world peace.",
    "I can see why Russia feels <br> threatened by the West.",
    "Would you say that your general opinion <br> of the NATO is very positive, slightly positive, neither positive nor negative, slightly negative, or very negative?",
    "Ukraine should waive a NATO <br> membership if this would bring peace.",
    "Ukraine should not make <br> any concessions to achieve peace.",
    "Trading or deliveries of weapons <br> between countries should be prohibited.",
    "If a country is being attacked and <br> the aggressor is targeting civilians, <br> [country] should provide military support.",
    "If a country is being attacked and <br> the aggressor is targeting critical <br> infrastructure (e.g., hospitals or electricity <br> and water supply), [country] should provide military support.",
    "If a country is being attacked (without <br> actual fault) and the aggressor is taking <br> away its land, [country] should provide <br> military support."
  ),
  Scale_level = c(
    "Categorical with 5 levels: <br> Germany, UK, USA, France, Italy",
    "Continuous",
    "Categorical with 2 levels: <br> male and female",
    "Categorical with 3 levels: <br> left, middle, right",
    "Categorical: 6-point Likert scale",
    "Categorical: 7-point Likert scale <br> (<em>not scared at all</em> to <em>very scared</em>)",
    "Categorical: 4-point Likert scale <br> (<em>matters a lot</em> to <em>does not matter at all</em>)",
    "Categorical: 7-point Likert scale <br> (<em>do not agree at all</em> to <em>completely agree</em>)",
    "Categorical: 7-point Likert scale <br> (<em>do not agree at all</em> to <em>completely agree</em>)",
    "Categorical: 5-point Likert scale <br> (<em>very positive</em> to <em>very negative</em>)",
    "Categorical with 2 levels: yes and no",
    "Categorical with 2 levels: yes and no",
    "Categorical: 7-point Likert scale <br> (<em>do not agree at all</em> to <em>completely agree</em>)",
    "Categorical: 7-point Likert scale <br> (<em>do not agree at all</em> to <em>completely agree</em>)",
    "Categorical: 7-point Likert scale <br> (<em>do not agree at all</em> to <em>completely agree</em>)",
    "Categorical: 7-point Likert scale <br> (<em>do not agree at all</em> to <em>completely agree</em>)"
  )
)

knitr::kable(covs, 
             format = "html", 
             col.names = c("Covariates", "Scale Level"), 
             escape = FALSE,
             caption = "Covariates and corresponding scale levels used in the analyses.")

@@

# Results

In @fig-amces we present the AMCEs estimated by averaging the IMCEs calculated using the cjbart model.

@@

## Integration of Results

For AMCEs, theoretically most favorable events served as baseline. 
As can be seen, increased attribute levels (i.e., less favourable events) were usually linked to significantly decreased levels of support. 
For example, increasing the risk of a nuclear strike from the reference level 'Not present (0%)' to 'Moderate (10%)' decreased the average probability of a participant choosing the latter profile by about -8.5%. 
The AMCE point estimates were in line with the AMCEs reported in CITE, which is why we refrain from an in-depth discussion here and refer the interested reader to CITE.
HIER WAS DAZU SCHREIBEN DAS WIR HÖHERE SEs HABEN? DAZU SCHREIBEN DIE HALT IN IHREM PAPER EH GAR NIX

@@

## Methodological Discussion

Discussion & Limitations -Tuning -Wie viele Covariates (inference vs. exploration) -Stabilität
